Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-05 paper/paper.tex
cite humphrey 2016, mcfee 2016

On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,kaminskyj2005jiis,benetos2006icassp,lostanlen2016ismir}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags'', encoded as binary outputs within some predefined label space.
Because such tags often belong to the publicly available metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music hosting platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.
Furthermore, supplementing user-generated content with the outcome of a crowdsourced annotation campaign  allows an explicit verification of instrument tags.
For instance, the Open-MIC dataset, maintained by the Community for Open and Sustainable Music Information Research (COSMIR), comprises a vast corpus of X polyphonic music recordings spanning X instruments, as a derivative of the Free Music Archive (FMA) dataset.
Another example is the Medley-solos-DB dataset, which comprises X monophonic excerpts from 8 instruments, as a derivative of the MedleyDB dataset of multitrack music.
Over the past decade, the surge of these large digital audio collections, together with the democratization of high-performance computing on dedicated hardware, has spurred the development of deep learning techniques, and notably deep convolutional networks, in music instrument recognition.
We refer to X for a recent review of the state of the art in this domain.

>>>>

On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,kaminskyj2005jiis,benetos2006icassp,lostanlen2016ismir}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags'', encoded as binary outputs within some predefined label space.
Because such tags often belong to the publicly available metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music hosting platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.
Furthermore, supplementing user-generated content with the outcome of a crowdsourced annotation campaign  allows an explicit verification of instrument tags.
For instance, the Open-MIC dataset \cite{humphrey2016ismir}, maintained by the Community for Open and Sustainable Music Information Research (COSMIR) \cite{mcfee2016ismir}, comprises a vast corpus of X polyphonic music recordings spanning X instruments, as a derivative of the Free Music Archive (FMA) dataset.
Another example is the Medley-solos-DB dataset, which comprises X monophonic excerpts from 8 instruments, as a derivative of the MedleyDB dataset of multitrack music.
Over the past decade, the surge of these large digital audio collections, together with the democratization of high-performance computing on dedicated hardware, has spurred the development of deep learning techniques, and notably deep convolutional networks, in music instrument recognition.
We refer to X for a recent review of the state of the art in this domain.
